A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-08 body/results.tex
results updated

\subsection{Performance analysis} \label{sec:perf}
To analyze performance, for each considered scenario, we ran the simulation 100 times.
We measured the computation time spent in each aspect of the algorithm, and also analyzed the success
rate obtained for each scenario.

@@

For each scenario, one can observe that the average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. In some cases such as the stair climbing, this computation time is actually negligeable. 
Considering the repartition of the computation time, it appears that the majority of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state of the art IK solutions, we believe there is room
for improving the performances of the algorithm.

>>>>

\subsection{Performance analysis} \label{sec:perf}
To analyze performance, for each considered scenario, we ran the simulation 1000 times.
We measured the computation time spent in each aspect of the algorithm, and also analyzed the success
rate obtained for each scenario.

@@

\subsection{Computation times}
For each scenario, one can observe that the average computation time for one single step is largely below the second,
thus allowing to consider interactive applications. In some cases such as the stair climbing, this computation time is actually negligeable. 
Considering the repartition of the computation time, it appears that the majority of the time is spent performing inverse kinematics.
This is not surprising considering the number of calls to the methods: IK is used intensively to maintain contact continuity between two postures; 
it is also applied every time a new candidate needs to be evaluated. However regarding state of the art IK solutions, we believe there is room
for improving the performances of the algorithm.

\subsection{Success rates times}
TODO contact generation 95 %.
